Tracing the Hercules stream around the Galaxy

### 2010-05-19 tex/hercules.tex
groups-simulations: abstract tweak

\begin{abstract}
It has been proposed that the Hercules stream, a group of co-moving
stars in the Solar neighborhood offset from the bulk of the velocity
distribution, is the result of resonant interactions between stars in
the outer disk and the Galactic bar. Only seen so far in the immediate
Solar neighborhood, I predict the distribution of stellar velocities
and the run of the Hercules stream as a function of location in the
Galactic disk in a simple model for the Galaxy and the bar that
produces the observed Hercules stream. I further show that the
Hercules feature is strong enough that it can be unambiguously
detected in the distribution of line-of-sight velocities in selected
directions. I quantify the most promising lines-of-sight for the
detection of the Hercules stream in radial velocities: The most
promising directions to target are at $l \geq 250^{\circ}$. The
predictions presented here are only weakly affected by distance
uncertainties, assumptions about the distribution function of the old
stellar disk, and the details of the Galactic potential including the
effect of spiral structure; \Gaia\ and future spectroscopic surveys of
the Galactic disk will be able to robustly test the origin of the
Hercules stream and constrain the properties of the Galactic bar.
\end{abstract}

>>>>

\begin{abstract}
It has been proposed that the Hercules stream, a group of co-moving
stars in the Solar neighborhood offset from the bulk of the velocity
distribution, is the result of resonant interactions between stars in
the outer disk and the Galactic bar. Only seen so far in the immediate
Solar neighborhood, I predict the distribution of stellar velocities
and the run of the Hercules stream as a function of location in the
Galactic disk in a simple model for the Galaxy and the bar that
produces the observed Hercules stream. I further show that the
Hercules feature is strong enough that it can be unambiguously
detected in the distribution of line-of-sight velocities in selected
directions. I quantify the most promising lines-of-sight for detection
in radial velocities: The most promising directions to target are at
$l \geq 250^{\circ}$. The predictions presented here are only weakly
affected by distance uncertainties, assumptions about the distribution
function of the old stellar disk, and the details of the Galactic
potential including the effect of spiral structure; \Gaia\ and future
spectroscopic surveys of the Galactic disk will be able to robustly
test the origin of the Hercules stream and constrain the properties of
the Galactic bar.
\end{abstract}
